% ICIP 2026 Grand Challenge — ClearSAR Track 1
% Two-page extended abstract (spconf.sty + IEEEbib.bst, per author kit)

\documentclass{article}
\usepackage{spconf,amsmath,amssymb,graphicx,booktabs}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}

\title{RFI DETECTION IN SENTINEL-1 SAR IMAGERY VIA PSEUDO-LABEL
DISTILLATION AND MULTI-RESOLUTION ENSEMBLE}

\name{Anas Elghoudane}
\address{Independent Researcher (\emph{UdeM AI} team)\\
\texttt{anaselghoudane@gmail.com}}

\begin{document}
\ninept
\maketitle

\begin{abstract}
We describe the \emph{UdeM AI} team's solution to the ESA ClearSAR
Track~1 Grand Challenge: Radio-Frequency Interference (RFI) detection
in Sentinel-1 SAR quicklooks. The pipeline combines a YOLO26x base
detector with a pixel-space Normalised Wasserstein Distance (NWD)
regression loss, pseudo-label distillation from a multi-source ensemble
teacher onto the unlabelled test imagery, multi-resolution test-time
augmentation (TTA) fused by Weighted Box Fusion (WBF), and a selective
cross-fold ensemble that drops the domain-overlapping fold. The final
submission reaches 0.4776 mAP$_{50\text{-}95}$ on the held-out test
set, 28th of 172 teams. We report two measurements. On a leak-isolated
meta-validation set the distilled student source gains $+0.077$
mAP$_{50\text{-}95}$ over a cold baseline; on the held-out test set the
same source is redundant with the ensemble teacher, and the full
distillation--TTA--blend stack adds only $+0.0021$ over the teacher
alone. The gap between the two is the main result.
\end{abstract}

\begin{keywords}
Ensemble, pseudo-label distillation, radio-frequency interference,
SAR imagery, small object detection.
\end{keywords}

\section{TASK AND DATA}
\label{sec:task}

The ESA ClearSAR Track~1 Grand Challenge \cite{clearsar2026} frames
RFI detection in Sentinel-1 quicklooks as a COCO-style object
detection task with mAP averaged over IoU 0.50--0.95. The labelled
set contains 3{,}154 images; 786 test images are held out by the
organisers and scored by the challenge platform from a zipped
COCO-format JSON of detections. RFI appears as thin horizontal stripes (median height
$\approx$10\,px, median width $\approx$140\,px) in variable-size RGB
quicklooks (median $\approx$515$\times$342\,px), with a median
per-box aspect ratio of $\approx$8:1. Three constraints follow:
IoU-based regression gives no gradient for non-overlapping thin boxes;
SAR side-looking geometry breaks horizontal symmetry, so flip TTA is
disabled (H-flip costs $-6.5\%$ \cite{oliver2004sar}); and inference
resolutions above 640\,px amplify speckle relative to signal. The
five-fold split is used to \emph{construct} diverse ensemble members,
not as an out-of-fold generalisation estimator: cross-fold validation
mAPs are leaked (each fold detector has seen the other folds' held-out
images) and are never used for model selection. We evaluate on two
separate sets: a 401-image leak-isolated meta-validation set sampled
from the fold-0 validation pool (seed 42), used as a single-model gate,
and the official held-out test set, used for model selection and final
reporting.

\section{METHOD}
\label{sec:method}

\begin{figure*}[t]
\centering
\setlength{\fboxsep}{3pt}
\scriptsize
\begin{tabular}{@{}c@{$\,\to\,$}c@{$\,\to\,$}c@{$\,\to\,$}c@{$\,\to\,$}c@{$\,\to\,$}c@{$\,\to\,$}c@{}}
\fbox{\parbox[c][12mm][c]{17mm}{\centering YOLO26x base\\5 folds\\CLAHE\,+\,NWD}} &
\fbox{\parbox[c][12mm][c]{15mm}{\centering V12 teacher\\WBF\\ensemble}} &
\fbox{\parbox[c][12mm][c]{17mm}{\centering Pseudo-label\\786 test imgs\\conf\,$\ge$\,0.75}} &
\fbox{\parbox[c][12mm][c]{17mm}{\centering Student FT\\$f\!\in\!\{1,2,4\}$\\freeze 10}} &
\fbox{\parbox[c][12mm][c]{18mm}{\centering Multi-res TTA\\608/640/\\672/704\,+\,WBF}} &
\fbox{\parbox[c][12mm][c]{17mm}{\centering Cross-fold WBF\\drop $f_0$\\$\to S^{*}$}} &
\fbox{\parbox[c][12mm][c]{19mm}{\centering Blend $w{=}0.25$\\$S^{*}\!\oplus$\,V12\\$\to$ V17 (0.4776)}} \\
\end{tabular}
\caption{Pipeline. A YOLO26x base detector (CLAHE input, pixel-space
NWD loss) is trained per fold; the V12 pre-distillation ensemble
pseudo-labels the 786 test images; per-fold students are fine-tuned
on the fold-augmented data, run multi-resolution TTA fused by WBF,
fused across folds (dropping the domain-overlapping fold~0) into a
super-source $S^{*}$, and blended with V12 at $w{=}0.25$.}
\label{fig:pipeline}
\end{figure*}

The pipeline (Figure~\ref{fig:pipeline}) has four stages.

\textbf{Base detector.} YOLO26x \cite{ultralytics2024yolo11}
($\approx$59\,M parameters, COCO pre-trained, no P2 head) trained
with a CIoU\,+\,NWD box loss
$\mathcal{L}_{\mathrm{box}} = (1{-}\alpha)\mathcal{L}_{\mathrm{CIoU}}
{+}\alpha\mathcal{L}_{\mathrm{NWD}}$ at $\alpha{=}0.5$, with NWD
\cite{wang2021nwd} computed in pixel space (normalisation constant
$C{=}12.8$\,px). Ultralytics evaluates the box loss on coordinates
normalised to the network input, so we rescale the positive boxes to
pixel units before computing NWD; otherwise $C$ is far too large, the
similarity saturates, and the gradient vanishes in the small-height
regime characteristic of RFI ($\approx$10\,px median).
Images are pre-processed with CLAHE (clip 3.0, $8\times8$ tiles) on
the LAB L-channel. Horizontal and vertical flips are disabled.
Training uses MuSGD for up to 100 epochs (patience 15) at 640\,px,
batch 32, $\eta_0{=}10^{-3}$ decaying linearly to $10^{-5}$.

\textbf{Pseudo-label distillation.} The teacher (V12) is our
strongest pre-distillation ensemble: a single-stage WBF
\cite{solovyev2021wbf} over multiple YOLO26x fold and
multi-resolution-TTA sources together with one RF-DETR-Large
\cite{roboflow2024rfdetr} fold checkpoint at weight $1.5\times$,
fused with $\tau{=}0.70$ and \texttt{conf\_type}=max. V12 scores
0.4755 on the held-out test set. The teacher is applied to the 786
unlabelled test images with confidence threshold 0.75 (max 20
boxes/img), producing 600 pseudo-labelled images. For each fold
$f\in\{1,2,4\}$, a student is fine-tuned from the per-fold base on
the fold-augmented dataset with AdamW \cite{loshchilov2019adamw}
($\eta_0{=}10^{-4}$, \texttt{freeze}=10, 15 epochs, batch 24, same
NWD blend). Fold 0 is omitted because its base partition overlaps the
meta-validation pool.

\textbf{Multi-resolution TTA and fusion.} Each student is inferred at
$\mathcal{I}=\{608,640,672,704\}$\,px; WBF across resolutions per
fold yields one TTA source. The three per-fold TTA sources are then
fused with equal weights into a super-source $S^{*}$. The final
submission V17 is the two-source WBF blend $D_{\mathrm{final}} =
\mathrm{WBF}(D_{\mathrm{V12}}, S^{*}; w{=}(1.0, 0.25), \tau{=}0.70)$.

\section{RESULTS AND DISCUSSION}
\label{sec:results}

\begin{table}[t]
\centering
\caption{\textbf{(a)} Construction of the student super-source $S^{*}$
on the 401-image leak-isolated meta-validation set (single-source;
reproducible from archived predictions). \textbf{(b)} Contribution on
the official held-out test set, the only leak-free measurement for the
full pipeline (V12 is leaked on meta-validation).}
\label{tab:ablation}
\small
\begin{tabular}{lcc}
\toprule
\multicolumn{3}{l}{\textbf{(a) Meta-validation (student source only)}}\\
\textbf{Configuration} & \textbf{mAP$_{50\text{-}95}$} & $\Delta$ \\
\midrule
Cold fold-0 baseline                  & 0.394 & --- \\
Pseudo-FT student, fold 4             & 0.434 & $+0.040$ \\
+ Multi-res TTA (4 res, WBF)          & 0.469 & $+0.035$ \\
+ 3-fold WBF (drop $f_0$) $= S^{*}$   & 0.471 & $+0.002$ \\
\midrule
\multicolumn{3}{l}{\textbf{(b) Held-out test (full pipeline)}}\\
\textbf{Configuration} & \textbf{mAP$_{50\text{-}95}$} & $\Delta$ \\
\midrule
Plain 5-fold WBF ensemble             & 0.4720 & --- \\
Teacher V12                           & 0.4755 & $+0.0035$ \\
Full pipeline V17                     & \textbf{0.4776} & $+0.0021$ \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:ablation}(a) decomposes the student source:
pseudo-distillation is the largest single component ($+0.040$), as the
soft signal in the teacher's confidence scores compensates for the
small training set; multi-resolution TTA adds $+0.035$ because thin
stripes a few pixels tall are resolved unevenly by YOLO's strided
feature pyramid at any single input size; dropping the
domain-overlapping fold-0 is net-positive because correlated
predictions drag the WBF consensus. Small-box accuracy tracks the same
chain (AP$_S$ $0.356\!\to\!0.418$); AP$_{75}$ stays the weakest column
($0.522$ vs $0.752$ at AP$_{50}$), placing the residual error at high
IoU. Table~\ref{tab:ablation}(b) measures transfer: on the held-out test set the full stack adds only
$+0.0021$ over the teacher and $+0.0056$ over a plain 5-fold ensemble.
The $+0.077$ student source is redundant with the teacher, which
already encodes the same multi-fold knowledge; the meta-validation
ceiling (0.515) is itself unreachable there because V12 is leaked on
that split. Pushing further regresses: blend weight $w{=}0.375$ gives
0.4768, and a second-generation pseudo-FT blend gives 0.4566, below the
teacher. Intermediate stages were scored only on meta-validation, as
official submissions were rate-limited to one per 12\,h.

\textbf{Negative results.} A second architectural family (RF-DETR)
plateaued at $+0.0002$ across six checkpoint--weight variants;
D-FINE-X \cite{peng2024dfine} fine-tuned on fold~0 for 10 epochs
reached $3\times10^{-4}$ mAP, suggesting DETR-family decoders with
different matching \cite{huang2024deim} would need substantially
more epochs to adapt to the elongated geometry of RFI; inference-only
SAHI \cite{akyon2022sahi} at 320-px tiles regressed $-0.085$,
fragmenting long horizontal stripes at tile boundaries; and
temperature-scaled calibration was at most $+0.0002$.

\section{CONCLUSION}
\label{sec:conclusion}

The final pipeline reaches 0.4776 mAP$_{50\text{-}95}$ on the held-out
test set, placing the \emph{UdeM AI} team 28th of 172 teams in ESA
ClearSAR Track~1, on a single cloud NVIDIA A100 GPU. On unseen SAR data
a quality-weighted multi-fold ensemble teacher recovers most of the
attainable accuracy, and the distillation--TTA--blend stack adds little
beyond it. The largest remaining gap is at high IoU thresholds, where
sub-pixel height accuracy dominates and a 640-px input under-resolves
the median $\approx$10-px stripe; sliced \emph{training} at 320-px
tiles is the most promising next step.

\bibliographystyle{IEEEbib}
\begin{thebibliography}{99}

\bibitem{clearsar2026}
European Space Agency,
``ClearSAR Track 1: Radio-frequency interference detection in
Sentinel-1 quicklook imagery,''
Challenge specification, 2026.

\bibitem{oliver2004sar}
C.~Oliver and S.~Quegan,
\emph{Understanding Synthetic Aperture Radar Images}.
SciTech Publishing, 2004.

\bibitem{ultralytics2024yolo11}
G.~Jocher and J.~Qiu,
``Ultralytics YOLO26,''
\url{https://github.com/ultralytics/ultralytics}, 2026.

\bibitem{wang2021nwd}
J.~Wang, C.~Xu, W.~Yang, and L.~Yu,
``A normalized Gaussian Wasserstein distance for tiny object
detection,''
\emph{arXiv:2110.13389}, 2021.

\bibitem{solovyev2021wbf}
R.~Solovyev, W.~Wang, and T.~Gabruseva,
``Weighted boxes fusion,''
\emph{Image and Vision Computing}, vol.~107, p.~104117, 2021.

\bibitem{roboflow2024rfdetr}
Roboflow,
``RF-DETR: A real-time transformer-based object detector,''
\url{https://github.com/roboflow/rf-detr}, 2024.

\bibitem{loshchilov2019adamw}
I.~Loshchilov and F.~Hutter,
``Decoupled weight decay regularization,''
in \emph{Proc. ICLR}, 2019.

\bibitem{peng2024dfine}
Y.~Peng, H.~Li, P.~Wu, Y.~Zhang, X.~Sun, and F.~Wu,
``D-FINE: Redefine regression task of DETR as fine-grained
distribution refinement,''
\emph{arXiv:2410.13842}, 2024.

\bibitem{huang2024deim}
S.~Huang, Z.~Lu, X.~Cun, Y.~Yu, X.~Zhou, and X.~Shen,
``DEIM: DETR with improved matching for fast convergence,''
\emph{arXiv:2412.04234}, 2024.

\bibitem{akyon2022sahi}
F.~C. Akyon, S.~O. Altinuc, and A.~Temizel,
``Slicing aided hyper inference and fine-tuning for small object
detection,''
in \emph{Proc. IEEE ICIP}, 2022, pp.~966--970.

\end{thebibliography}

\end{document}
